### 2018-03-17 paper/5-implementations.tex
Minor changes

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Determine whether a trace is relevant to the current state
traceMatch :: (Monad m, Eq k)
    => (k -> Hash v -> m Bool) -> k -> [Trace k v] -> m [Hash v]
traceMatch check key ts = mapMaybeM f ts
    where f (Trace k dkv v) = do
                b <- return (key == k) &&^ allM (uncurry check) dkv
                return $ if b then Just v else Nothing
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Recursive dependency strategy
recursive :: Eq k => (k -> (k -> State (Store i k v, [k]) v)
                  -> State (Store i k v, [k]) (v, [k])
                  -> State (Store i k v, [k]) ())
                  -> Build Monad i k v
recursive process task key store = fst $ execState (ensure key) (store, [@@])
    where
        ensure key = do
            let fetch k = do ensure k; gets (getValue k . fst)
            done <- gets snd
            when (key `notElem` done) $ do
                modify $ \(s, done) -> (s, key:done)
                case track task fetch key of
                    Nothing -> return ()
                    Just act -> process key fetch act
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Shake build system
shake :: (Eq k, Hashable v) => Build Monad [Trace k v] k v
shake = recursive $ \key fetch act -> do
    traces <- gets (getInfo . fst)
    poss <- traceMatch (\k v -> (==) v . hash <$> fetch k) key traces
    current <- gets (getHash key . fst)
    when (current `notElem` poss) $ do
        (v, ds) <- act
        modify $ \(s, done) ->
            let t = Trace key [(d, getHash d s) | d <- ds] (getHash key s)
            in (putInfo (t : getInfo s) (putValue key v s), done)

@@

The differences from \hs{bazel} are minor - the dependency scheme has changed from \hs{topological} to \hs{recursive}, and thus the dependency keys \hs{dk} are captured from the action rather than in advance, the transient state has gained a list of keys, and the checking calls \hs{fetch} to get the result instead of accessing the store directly.

@@

In the examples above, we have used \hs{[Trace}~\hs{k}~\hs{v]} to capture a list of traces -- however, using a list necessarily means that finding the right trace takes $O(n)$. For each of the \hs{Trace} based systems it is possible to devise a smarter representation, which we sketch below. Note that these implementations do not avoid calls to \hs{compute}, merely overheads in the build system itself.

>>>>

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Determine whether a trace is relevant to the current state
traceMatch :: (Monad m, Eq k)
    => (k -> Hash v -> m Bool) -> k -> [Trace k v] -> m [Hash v]
traceMatch check key ts = mapMaybeM f ts
    where f (Trace k dkv v) = do
                b <- return (key == k) &&^ allM (uncurry check) dkv
                return $ if b then Just v else Nothing
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Recursive dependency strategy
recursive :: Eq k => (k -> (k -> State (Store i k v, [k]) v)
                  -> State (Store i k v, [k]) (v, [k])
                  -> State (Store i k v, [k]) ())
                  -> Build Monad i k v
recursive process task key store = fst $ execState (ensure key) (store, [@@])
    where
        ensure key = do
            let fetch k = do ensure k; gets (getValue k . fst)
            done <- gets snd
            when (key `notElem` done) $ do
                modify $ \(s, done) -> (s, key:done)
                case track task fetch key of -- track is defined in @\S\ref{secdeps}@
                    Nothing -> return ()
                    Just act -> process key fetch act
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Shake build system
shake :: (Eq k, Hashable v) => Build Monad [Trace k v] k v
shake = recursive $ \key fetch act -> do
    traces <- gets (getInfo . fst)
    poss <- traceMatch (\k v -> (==) v . hash <$> fetch k) key traces
    current <- gets (getHash key . fst)
    when (current `notElem` poss) $ do
        (v, ds) <- act
        modify $ \(s, done) ->
            let t = Trace key [(d, getHash d s) | d <- ds] (getHash key s)
            in (putInfo (t : getInfo s) (putValue key v s), done)

@@

The differences from \hs{bazel} are minor~--~the dependency scheme has changed
from \hs{topological} to \hs{recursive}, and thus the dependency keys \hs{dk}
are captured from the action rather than in advance, the transient state has
gained a list of keys, and the checking calls \hs{fetch} to get the result
instead of accessing the store directly.

@@

In the examples above, we have used \hs{[Trace}~\hs{k}~\hs{v]} to capture a list
of traces~--~however, using a list necessarily means that finding the right trace
takes $O(n)$. For each of the \hs{Trace} based systems it is possible to devise
a smarter representation, which we sketch below. Note that these implementations
do not avoid calls to \hs{compute}, merely overheads in the build system itself.

### 2018-03-17 paper/6-engineering.tex
Minor changes

\noindent
Handling such tasks is possible in our framework, but requires an adjustment of
the correctness definition (\S\ref{sec-build-correctness}): instead of requiring
that the result of recomputing the \hs{task} matches the value stored in the \hs{result}:
\[
\hs{Just}~\hs{(}\hs{getValue}~\hs{k}~\hs{result)}~\hs{==}~\hs{compute}~\hs{task}~\hs{result}~\hs{k}\]
\noindent
we now require that \hs{result} contains \emph{one possible result of recomputing}
the \hs{task}:
\[
\hs{Just}~\hs{(}\hs{getValue}~\hs{k}~\hs{result)}~\hs{`elem`}~\hs{compute}~\hs{task}~\hs{result}~\hs{k}
\]

>>>>

\noindent
Handling such tasks is possible in our framework, but requires an adjustment of
the correctness definition (\S\ref{sec-build-correctness}): instead of requiring
that the result of recomputing the \hs{task} matches the value stored in the \hs{result}:
\[
\hs{Just}~\hs{(}\hs{getValue}~\hs{k}~\hs{result)}~\hs{==}~\hs{compute}~\hs{task}~\hs{result}~\hs{k}\]
\noindent
we now require that \hs{result} contains \emph{one possible result of recomputing}
the \hs{task}:
\[
\hs{Just}~\hs{(}\hs{getValue}~\hs{k}~\hs{result)}~\hs{`elem`}~\hs{computeND}~\hs{task}~\hs{result}~\hs{k}
\]
where
\hs{computeND}~\hs{::}~\hs{Task}~\hs{MonadPlus}~\hs{k}~\hs{v}~\hs{->}~\hs{Store}~\hs{i}~\hs{k}~\hs{v}~\hs{->}~\hs{k}~\hs{->}~\hs{Maybe}~\hs{[@@v]}
returns the list of all possible results of the \hs{task} instead of just one
value (`ND' stands for `non-deterministic').
% (a possible implementation chooses
% \hs{f}~\hs{=}~\hs{ListT}~\hs{Identity}~\hs{[@@v]}).
